### 2012-08-21 docs/compilers/compilers.tex
compiler notes

Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor, multilevel runs ({\tt toy\_convect} on 4
processors, with {\tt inputs\_2d\_ml.test} for instance).  The symptom
is a crash during initialization with the message that ``message sizes
do not match across processes in the collective'' in a {\tt
parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue
seems to be a multiplication error in computing the size to allocate
{\tt bxs}.  The bug is not present when you compile in debug mode, so
it seems to be related to optimization.
\item gfortran 4.7.1 (prerelease) seems to have fixed the above issue.
\end{itemize}

>>>>

\begin{itemize}
\item Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.
\item Cray 5.12 compiles and runs \maestro\ fine on hopper (8/21/12).
\end{itemize}

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.4.3 dies with an out of bounds error in multigrid for
2+ level runs with effective 128$^3$ resolution or better.
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor, multilevel runs ({\tt toy\_convect} on 4
processors, with {\tt inputs\_2d\_ml.test} for instance).  The symptom
is a crash during initialization with the message that ``message sizes
do not match across processes in the collective'' in a {\tt
parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue
seems to be a multiplication error in computing the size to allocate
{\tt bxs}.  The bug is not present when you compile in debug mode, so
it seems to be related to optimization.
\item gfortran 4.7.1 (prerelease) seems to have fixed the above issue,
but now wdconvect with 2-level, effective 768$^3$ dies due to an
unknown seg fault at the beginning of the run.
\end{itemize}
